---
title: "MLforBrCa Supplementary Material"
author: "Xiaonan Liu"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: show
    highlight: kate
---

```{r setup, include=FALSE,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(include=TRUE, echo=FALSE)

library(kableExtra)
library(knitr)
library(yaml)
library(here)
library(ggplot2)
library(tidyr)
library(DiagrammeR)
library(DiagrammeRsvg)
library(magrittr)
library(svglite)
library(rsvg)
library(png)
library(grid)
library(dplyr)
library(survival)
library(survminer)
library(naniar)
library(summarytools)
library(rsample)      # data splitting 
library(gbm)          # basic implementation
library(xgboost)      # a faster implementation of gbm
library(caret)        # an aggregator package for performing many machine learning models
library(h2o)          # a java-based platform
library(pdp)          # model visualization
library(lime)         # model visualization
library(vip)          # Feature importance visualisation
library(rms)
library(mice)
library(shiny)
library(gtools)
library(ggeffects)
library(mitml)
library(rcompanion)

# Specify the markdown format for knitr tables, otherwise they're not compatible with kableExtra
options(knitr.kable.NA='', knitr.table.format = "html")
options(kableExtra.auto_format = FALSE)
options(rstudio.connectionObserver.errorsSuppressed = TRUE)
# Set the root directory to the project directory (otherwise knitr works in the directory of the Rmd file by default)
knitr::opts_knit$set(root.dir = here::here())

# Load the project config file for filepaths etc
config = yaml.load_file(here::here("./config.yml"))
source(here::here(config$functions$JC))

#-------------------------------------------------------------------------------------------------------------------
# Setup

figure <- 1
table <- 1
suppfig <- 1
footnote_no <- 1


tot_train<-readRDS(here::here(file.path(config$data$derived,"tot_train.rds")))
tot_test<-readRDS(here::here(file.path(config$data$derived,"tot_test.rds")))

xgboost_SHAP<-read.csv(here::here(file.path(config$outputs$outputs,"XGBoost_SHAP.csv")))

load(here::here(file.path(config$data$derived,"imp_post.rds")))
load(here::here(file.path(config$data$derived,"imp_post_derived.rds")))

```

```{r Data extraction,include=FALSE}

source(file.path(config$scripts$cleaning, "dataset_generator.R"))

pretty_names <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type="list")
pretty_func <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type = "function")

pretty_names$TEU_Alc_DailyAlcUnits="Daily alcohol intake"
pretty_names$TEU_BrCa_100k_PRS="$$PRS_{120k}$$"
pretty_names$TEU_BrCa_313_PRS="$$PRS_{313}$$"
pretty_names$TEU_BrCa_100k_PRS_quintiles="$$PRS_{120k}$$ quintiles"
pretty_names$TEU_BrCa_313_PRS_quintiles="$$PRS_{313}$$ quintiles"
pretty_names$TEU_BrCa_313_PRS_percent="$$PRS_{313}$$ percentiles"
pretty_names$TEU_BrCa_100k_PRS_quint=pretty_names$TEU_BrCa_100k_PRS_quintiles
pretty_names$TEU_BrCa_313_PRS_quint=pretty_names$TEU_BrCa_313_PRS_quintiles
pretty_names$G03FA="HRT user"
```

# Introduction

This report documents the code for supplementary material.

# Baseline Model

**N=`r nrow(MI_data)`** with `r sum(MI_data$TEU_BrCa_status)` breast cancer cases.

We built the Cox model: 

* Baseline model: BrCa ~ Established RFs 

(XL): PRS were categorised into quintiles. Weekly alcohol intake was divided by 7 to reflect daily alcohol intake.

```{r Baseline model}

eRFs <- c("TEU_BrCa_100k_PRS_quint","TEU_BrCa_313_PRS_quint","TEU_BaC_AgeAtRec","Imp_BodyFatMass","FSF_MenopauseAge","TEU_Alc_DailyAlcUnits","TEU_FirstBirthAgeCat","TEU_FaH_BrCa" ,  "PhA_METsWkAllAct" ,"G03FA", "FSF_PeriodAge","BBC_IGF1_Result" ,"BBC_TES_Result", "FSF_NLiveBirths" ,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(eRFs, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_baseline <- printMIresults(df=comp_long1$data, varlist=eRFs, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#View(routput_baseline)
#kable(routput_baseline)%>%
  #kable_styling(bootstrap_options = c("striped", "hover")) 
```


```{r Analysis Diag,eval=FALSE}

pha_plots<-list() #save PHA plot for each imputation
vifs<-list() #save multicollinearity results

imp1=comp_long1

for (i in 1:imp1$m) {
  ## 1. PHA
  pha_plots[[i]]<-ggcoxzph(cox.zph(rmodel$analyses[[i]]))
  
  ## 2. Multicollinearity
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
  vifs[[i]]<-rms::vif(cph(formula,data=complete(comp_long1,i)))
  cat("Imputation",i,", Any VIF above>10:",any(vifs[[i]]>10),'\n')
  
}

# Use shinyapp for better visualisation

choices = 1:imp1$m

names(choices) <- paste("Imputation",1:imp1$m)
shinyApp(
  ui = fluidPage(
    titlePanel("PHA plot on each imputation"),
    sidebarPanel(
      selectInput("plot", "Choose plot:", choices=choices),
      hr()),
      #helpText("Trail plots")),
    plotOutput("mainplot")
  ),
  server = function(input, output) {
    output$mainplot<-renderPlot({
      i<- as.integer(input$plot)
      pha_plots[[i]]
    }, height = 1000, width = 2000)
  }
)


```

Concordance index of baseline model in each imputation dataset: 

```{r}

post_long1<-complete(comp_long1,"long")

pool<-post_long1%>%
  group_by(.imp)%>%
  summarise(.,`C-index`=concordance(coxph(formula=as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")))$concordance)

pool
```



# New Model 1 (Add new vars)

* New Model 1: BrCa ~ Established RFs + New potential RFs

```{r}
# Transform the variables fitted in the model
imp_features=replace(imp_features,imp_features=="TEU_Alc_WeeklyAlcUnits","TEU_Alc_DailyAlcUnits")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_100k_PRS","TEU_BrCa_100k_PRS_quint")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_313_PRS","TEU_BrCa_313_PRS_quint")

```

```{r New Model 1}

varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel_m1 <- with(comp_long1, coxph(as.formula(formula)))

routput_m1 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel_m1)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#kable(routput_m1)%>%
 # kable_styling(bootstrap_options = c("striped", "hover")) 
```

```{r,eval=FALSE}

pha_plots<-list() #save PHA plot for each imputation
vifs<-list() #save multicollinearity results

imp1=comp_long1

for (i in 1:imp1$m) {
  ## 1. PHA
  pha_plots[[i]]<-ggcoxzph(cox.zph(rmodel$analyses[[i]]))
  
  ## 2. Multicollinearity
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
  vifs[[i]]<-rms::vif(cph(formula,data=complete(comp_long1,i)))
  cat("Imputation",i,", Any VIF above>10:",any(vifs[[i]]>10),'\n')
  
}

# Use shinyapp for better visualisation

choices = 1:imp1$m

names(choices) <- paste("Imputation",1:imp1$m)
shinyApp(
  ui = fluidPage(
    titlePanel("PHA plot on each imputation"),
    sidebarPanel(
      selectInput("plot", "Choose plot:", choices=choices),
      hr()),
      #helpText("Trail plots")),
    plotOutput("mainplot")
  ),
  server = function(input, output) {
    output$mainplot<-renderPlot({
      i<- as.integer(input$plot)
      pha_plots[[i]]
    }, height = 1000, width = 2000)
  }
)

```


```{r merge}

# Merge baseline and New model1 analysis tgt
output<-full_join(routput_baseline,routput_m1,by=c("IDcol"))%>%
  select(Coefficient.y,HR.x,`95% CI.x`,p.x,HR.y,`95% CI.y`,p.y)%>%
  `colnames<-`(c("Coefficient","HR","95% CI","p","HR","95% CI","p"))

kable(output,caption = "Main Analyses: Association of potential RFs with BrCa")%>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_header_above(c(" " = 1,  "Baseline Model" = 3, "New Model 1" = 3))

```

```{r}

pool2<-post_long1%>%
  group_by(.imp)%>%
  summarise(.,`C-index`=concordance(coxph(formula=as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")))$concordance)

pool2

```

# Interaction Model 

From SHAP dependence plots: for older age (60+), having a relative higher PRS exaggerates age effect on developing breast cancer whereas for younger age (53-60), having a relative lower PRS exaggerate age effect on developing breast cancer.

Continue from New Model 1, we further added potential interaction, Age*PRS. PRS was categorised into quintiles while age kept as continuous.

* BrCa ~ Established  RFs + New RFs + Age*PRS

**BrCa 100k PRS**: 

```{r}
# 100k PRS * age
varlist <- c(imp_features,"TEU_BrCa_100k_PRS_quint:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_int1 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)

pander(routput_int1,caption="New model 1 + Age*BrCa 100k PRS (quintiles)")

```

```{r}
# Overall p-value


LR1<-anova(rmodel_m1,rmodel,method = 'D2',use = 'likelihood')

p1<-pretty_pval(LR1$out$`2 ~~ 1`$result[4])

```

Interaction p-value is `r p1`

Visual plots on relative hazard (based on one random imputation dataset): 'K:\\TEU\\MLforBrCa\\Stats_Outputs\\Marginal_PRS120k.png'



```{r int plots,eval=FALSE}
# Plot (Age*prs)

# Note: For some reason, the formula with paste above doesn't work in this loop!

predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result + TEU_BrCa_100k_PRS_quint:TEU_BaC_AgeAtRec +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BaC_AgeAtRec [all]","TEU_BrCa_100k_PRS_quint"))
})

# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)


plot(predictions[[1]])+
  labs(x=expression(bold("Age at recruitment, years")),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold(PRS["120k"]~quintiles)))+
  xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```

**BrCa 313 PRS**:

```{r}
# 313 PRS * age
varlist <- c(imp_features,"TEU_BrCa_313_PRS_quint:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_int2 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)


pander(routput_int2,caption="New Model 1 + BrCa 313 PRS")


```

```{r}
# Overall p-value

LR2<-anova(rmodel_m1,rmodel,method = 'D2',use = 'likelihood')

p2<-pretty_pval(LR2$out$`2 ~~ 1`$result[4])

```

Interaction p-value is `r p2`.

Visual plots on relative hazard (based on one random imputation dataset): 'K:\\TEU\\MLforBrCa\\Stats_Outputs\\Marginal_PRS313.png'


```{r BrCa 313 int plots,eval=FALSE}
# Plot (Age*prs)

# Note: For some reason, the formula with paste above doesn't work in this loop!

predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result + TEU_BrCa_313_PRS_quint:TEU_BaC_AgeAtRec +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BaC_AgeAtRec [all]","TEU_BrCa_313_PRS_quint"))
})

# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)

plot(predictions[[1]])+
  labs(x=expression(bold("Age at recruitment, years")),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold(PRS["313"]~quintiles)))+
  xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```


# Stratified Cox model by age groups

Categorised age in 3 groups: [40,53), [53,62), [62,70) and performed stratified cox model by 3 age groups: 

* BrCa ~ PRS + Genetic Array + First 10 genetic PCs

Note: Originally we wanted to categorise PRS into percentiles according to Mavaddat2019 (i.e. <1%, 1-5%, ...); however, due to sample size of each age group, we ran into model convergence issue.

**BrCa 100k PRS:**

```{r}

df<-tot_train%>%
  mutate(agecat=cut(TEU_BaC_AgeAtRec,
                       breaks = c(40, 53, 62, 70),
                       labels = c("[40,53)", "[53,62)", "[62,70)"),
                       right = FALSE
    ),
  TEU_BrCa_100k_PRS=TEU_BrCa_100k_PRS*115300*2,
  TEU_BrCa_313_PRS=TEU_BrCa_313_PRS*305*2,
  PRS_100k=quantcut(TEU_BrCa_100k_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')),
  PRS_313=quantcut(TEU_BrCa_313_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')))


# Relevel so that average is the ref
#df <- within(df, PRS_100k_tertile <- relevel(PRS_100k_tertile, ref = "Average"))
#df <- within(df, PRS_313_tertile <- relevel(PRS_313_tertile, ref = "Average"))

propped(table(df$agecat))

RFs<-c("PRS_100k","GeP_Array",paste0("GeP_PC_",1:10))

formula<-as.formula(paste0("Surv(TEU_BrCa_time,TEU_BrCa_status)~", 
                           paste(RFs, collapse="+")))

cox_results=lapply(split(df, df$agecat),
       FUN = function(DF) {
         
         coxph(formula, DF)
       })


```



```{r}

tab1=printcoxresults(df,varlist = "PRS_100k",modeloutput = cox_results$`[40,53)`,pretty_names = pretty_names,forplot = TRUE)

tab1$agegrp="[40,53)"


tab2=printcoxresults(df,varlist =  "PRS_100k",modeloutput = cox_results$`[53,62)`,pretty_names = pretty_names,forplot=TRUE)

tab2$agegrp="[53,62)"

tab3=printcoxresults(df,varlist =  "PRS_100k",modeloutput = cox_results$`[62,70)`,pretty_names = pretty_names,forplot=TRUE)

tab3$agegrp="[62,70)"

tab=rbind(tab1,tab2,tab3)

kable(tab,caption = "Hazard Ratio of BrCa 100k PRS in different age groups")%>%
 kable_styling(bootstrap_options = c("striped", "hover")) 

# Visualise PRS effect SC by age

ggplot(tab, aes(fill=factor(Levels,levels = c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')), y=HR_num, x=agegrp)) + 
    geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.2,
                 position=position_dodge(.9)) +
  labs(x="Age at recruitment, years (Categorical)",y="Hazard Ratio with 95% CI",title = "") + 
  scale_fill_discrete(name = expression(bold(PRS["120k"]~quintiles)))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```


**BrCa 313 PRS:**

```{r}

RFs<-c("PRS_313","GeP_Array",paste0("GeP_PC_",1:10))

formula<-as.formula(paste0("Surv(TEU_BrCa_time,TEU_BrCa_status)~", 
                           paste(RFs, collapse="+")))

cox_results=lapply(split(df, df$agecat),
       FUN = function(DF) {
         
         coxph(formula, DF)
       })


```


```{r}

tab1=printcoxresults(df,varlist = "PRS_313",modeloutput = cox_results$`[40,53)`,pretty_names = pretty_names,forplot = TRUE)

tab1$agegrp="[40,53)"


tab2=printcoxresults(df,varlist =  "PRS_313",modeloutput = cox_results$`[53,62)`,pretty_names = pretty_names,forplot=TRUE)

tab2$agegrp="[53,62)"

tab3=printcoxresults(df,varlist =  "PRS_313",modeloutput = cox_results$`[62,70)`,pretty_names = pretty_names,forplot=TRUE)

tab3$agegrp="[62,70)"

tab=rbind(tab1,tab2,tab3)

kable(tab,caption = "Hazard Ratio of BrCa 313 PRS in different age groups")%>%
 kable_styling(bootstrap_options = c("striped", "hover")) 

# Visualise PRS effect SC by age

ggplot(tab, aes(fill=factor(Levels,levels = c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')), y=HR_num, x=agegrp)) + 
    geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.2,
                 position=position_dodge(.9)) +
  labs(x="Age at recruitment, years (Categorical)",y="Hazard Ratio with 95% CI",title = "") + 
  scale_fill_discrete(name = expression(bold(PRS["313"]~quintiles)))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```

# Exclude first 2 yrs FU (Training)

To further investigate blood count, biochemistry, urine assays variables, we would like to restrict our analysis population to people with 2 or more years follow up and see if they are still significant. The logic behind this is to see if significance were due to reverse causation. 


Out of `r nrow(tot_train)` post-menopausal women, there were `r tot_train%>%filter(TEU_BrCa_time>=2)%>%nrow` with 2 or more years follow up.

```{r imp features}

imp_features<-c(
  xgboost_SHAP$Var_name[c(1:5,7:20)],
  # Because FaH of BrCa var name is in a different format
  "TEU_FaH_BrCa",
  # established RFs
  "PhA_METsWkAllAct", "G03FA","FSF_PeriodAge",
   "FSF_NLiveBirths" 
)


# Replace Father death age and age at first birth with the manipulated ones 

imp_features=replace(imp_features,imp_features=="TEU_FirstBirthAge","TEU_FirstBirthAgeCat")
imp_features=replace(imp_features,imp_features=="TEU_Alc_WeeklyAlcUnits","TEU_Alc_DailyAlcUnits")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_100k_PRS","TEU_BrCa_100k_PRS_quint")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_313_PRS","TEU_BrCa_313_PRS_quint")

```


```{r SA New Model 1}

# Transform to long first 
post.long <- mice::complete(comp_long1,"long",include = T)

post.long.sub <- post.long[which(post.long$TEU_BrCa_time >=2),]
# Post-hoc: Scale variables with HR CI (1,1) to show wider CI in forest plot

post.long.sub<-post.long.sub%>%
  mutate(
    TEU_Alc_DailyAlcUnits=TEU_Alc_WeeklyAlcUnits/7,
    )%>%
  group_by(.imp)%>%
  mutate(
    # Scale variables by mean and sd within each imp
    Imp_MetRate=scale_this(Imp_MetRate),
    Uri_Sodium=scale_this(Uri_Sodium),
    Uri_Creat=scale_this(Uri_Creat),
    BBC_ALP_Result=scale_this(BBC_ALP_Result),
    PhA_METsWkAllAct=scale_this(PhA_METsWkAllAct),
    TEU_BrCa_100k_PRS_quint=quantcut(TEU_BrCa_100k_PRS,q=5,labels = c('Q1: Lowest score','Q2','Q3','Q4','Q5: Highest score')),
    TEU_BrCa_313_PRS_quint=quantcut(TEU_BrCa_313_PRS,q=5,labels = c('Q1: Lowest score','Q2','Q3','Q4','Q5: Highest score'))
  )


# Create mids object
imp_post_sub <- as.mids(post.long.sub)

##
varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel <- with(imp_post_sub, coxph(as.formula(formula)))

routput_post_sub <- printMIresults(df=imp_post_sub$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)

pander(routput_post_sub)
```


```{r Diag,eval=FALSE}

pha_plots<-list() #save PHA plot for each imputation
vifs<-list() #save multicollinearity results

imp1=imp_post_sub

for (i in 1:imp1$m) {
  ## 1. PHA
  pha_plots[[i]]<-ggcoxzph(cox.zph(rmodel$analyses[[i]]))
  
  ## 2. Multicollinearity
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
  vifs[[i]]<-rms::vif(cph(formula,data=complete(imp_post_sub,i)))
  cat("Imputation",i,", Any VIF above>10:",any(vifs[[i]]>10),'\n')
  
}

# Use shinyapp for better visualisation

choices = 1:imp1$m

names(choices) <- paste("Imputation",1:imp1$m)
shinyApp(
  ui = fluidPage(
    titlePanel("PHA plot on each imputation"),
    sidebarPanel(
      selectInput("plot", "Choose plot:", choices=choices),
      hr()),
      #helpText("Trail plots")),
    plotOutput("mainplot")
  ),
  server = function(input, output) {
    output$mainplot<-renderPlot({
      i<- as.integer(input$plot)
      pha_plots[[i]]
    }, height = 1000, width = 2000)
  }
)



```

```{r forestplot,eval=FALSE}

# Change order of FaH so corresponding to the SHAP order
present=setdiff(imp_features,"TEU_FaH_BrCa")
present <- append(present, values = "TEU_FaH_BrCa", after = match("TEU_Alc_DailyAlcUnits", present) - 1)  

# Add unit to features 
pretty_names$BBC_TES_Result="Testosterone,nmol/L"
pretty_names$FSF_MenopauseAge="Age at menopause,years"
pretty_names$TEU_Alc_DailyAlcUnits="Daily alcohol intake,units"
pretty_names$BBC_BUN_Result="Plasma urea,mmol/L"
pretty_names$Imp_MetRate="Basal metabolic rate,KJ"
pretty_names$BBC_PHOS_Result="Plasma phosphate,mmol/L"
pretty_names$BBC_IGF1_Result="IGF-1,nmol/L"
pretty_names$Uri_Sodium="Sodium in urine,mmol/L"
pretty_names$BlA_RedBCCount="Red blood cell count,10^12/L"
pretty_names$BBC_AST_Result="Aspartate aminotransferase,U/L"
pretty_names$TEU_FirstBirthAgeCat="Age at first birth,years (Categorical)"
pretty_names$Uri_Creat="Creatinine (enzymatic) in urine,mcmol/L"
pretty_names$BlA_MonocytCount="Monocytes count,10^9/L"
pretty_names$Imp_BodyFatMass="Whole body fat mass,Kg"
pretty_names$BBC_ALP_Result="Alkaline phosphatase,U/L"
pretty_names$BBC_CRP_Result="C-reactive protein,mg/L"
pretty_names$FSF_PeriodAge="Age at menarche,years"
pretty_names$PhA_METsWkAllAct="Summed MET minutes per week"
pretty_names$TEU_BaC_AgeAtRec="Age at recruitment,years"


m1_forplot <- printMIresults(df=imp_post_sub$data, varlist=present, modeloutput=summary(pool(rmodel)),
                                pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE,forplot = TRUE)

cox_m1<-m1_forplot%>%
  # Create HR (95% CI)
  mutate(HR_CI=ifelse(is.na(L_CI),NA_character_,paste0(pretty_dp(HR_num,2)," ",pretty_confint(L_CI, U_CI, dp=2))))

cox_m1$HR_CI[is.na(cox_m1$HR_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- "1"
cox_m1$HR_num[is.na(cox_m1$HR_num) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$L_CI[is.na(cox_m1$L_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$U_CI[is.na(cox_m1$U_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1

# Hacky tweak so the cox model names correpsond to SHAP names
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{120k}$$ quintiles**"]="TEU_BrCa_100k_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{313}$$ quintiles**"]="TEU_BrCa_313_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**Family history of BrCa**"]="TEU_FaH_BrCa_Family history of BrCa"
cox_m1$IDcol[cox_m1$IDcol=="**Age at first birth,years (Categorical)**"]="TEU_FirstBirthAge"
cox_m1$IDcol[cox_m1$IDcol=="TEU_Alc_DailyAlcUnits"]="TEU_Alc_WeeklyAlcUnits"

# Add space for levels of categorical vars
cox_m1<-cox_m1%>%
  mutate(Coefficient=ifelse(!str_detect(Coefficient,fixed("**")),paste0("       ",Coefficient),Coefficient))


# Prepare SHAP 

shap<-xgboost_SHAP[1:20,]%>%
  select(Var_name,SHAP)%>%
  #mutate(norm_SHAP=(SHAP-min(SHAP))/(max(SHAP)-min(SHAP)))%>%
  mutate(SHAP_pretty=pretty_dp(SHAP,2))

#shap$Var_name[shap$Var_name=="TEU_FaH_BrCa_Family history of BrCa"]="TEU_FaH_BrCa"
#shap$Var_name[shap$Var_name=="TEU_BrCa_100k_PRS"]="TEU_BrCa_100k_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_BrCa_313_PRS"]="TEU_BrCa_313_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_FirstBirthAge"]="TEU_FirstBirthAgeCat"
#shap$Var_name[shap$Var_name=="TEU_Alc_WeeklyAlcUnits"]="TEU_Alc_DailyAlcUnits"
#shap$Var_name2=preparecoefflist_2col(df=comp_long1$data,varname = shap$Var_name,pretty_names = pretty_names)

# Left join 

cox_shap<-left_join(cox_m1,shap,by=c("IDcol"="Var_name"))%>%
  select(Coefficient,SHAP_pretty,HR_CI,p,HR_num,L_CI,U_CI)%>%
  mutate(summary=FALSE)%>%
  mutate(Coefficient=str_remove_all(Coefficient,fixed("**")))%>%
  add_row(Coefficient = "Features", SHAP_pretty="SHAP Value",HR_CI="HR (95% CI)",p="p-value", summary=TRUE,.before = 1)%>%
  rename(mean=HR_num,lower=L_CI,upper=U_CI)
  


# initialize plot
#tiff(file.path(config$outputs$outputs,"forestplot_A.tiff"),  units = "in", width = 7, height = 25, res = 300)

# make plot

tabletext <- list(
 c("Features",append(list(expression(PRS["120k"]~quintiles)),cox_shap$Coefficient[3:7]),append(list(expression(PRS["313"]~quintiles)),cox_shap$Coefficient[9:21])),
  c(list(expression(SHAP["ma"])),cox_shap$SHAP_pretty[2:21]),
  cox_shap$HR_CI[1:21],
  cox_shap$p[1:21]
)



cox_shap[1:21,]%>%
  forestplot(labeltext = tabletext, 
             is.summary = summary,
             clip = c(0.3, 2.8), 
             hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:5, col = "#000044") 
                               #"3" = gpar(lwd=1),
                               #"9" = gpar(lwd=1),
                               #"18" = gpar(lwd=1)
                               ),
             xlog = FALSE,
             boxsize=0.3,
             graph.pos=3,
             colgap=unit(3, 'mm'),
             graphwidth=unit(34, 'mm'),
             lwd.ci=2,
             lwd.xaxis=2,
             zero = 1,
             xticks = seq(0.5, 2.5, 0.5), 
             #mar = unit(rep(10, times = 4), "mm"),
             col = fpColors(box = "royalblue",
                            line = "darkblue", 
                            summary = "royalblue"))


# save plot
#dev.copy(png,file.path(config$outputs$outputs,"forestplot.png"))
#dev.off()

## Too long, has to be split into 2
#tiff(file.path(config$outputs$outputs,"forestplot_B.tiff"),  units = "in", width = 13, height = 50, res = 300)

tabletext <- list(
 cox_shap$Coefficient[c(1,22:nrow(cox_shap))],
  c(list(expression(SHAP["ma"])),cox_shap$SHAP_pretty[22:nrow(cox_shap)]),
  cox_shap$HR_CI[c(1,22:nrow(cox_shap))],
  cox_shap$p[c(1,22:nrow(cox_shap))]
)



# make plot
cox_shap[c(1,22:nrow(cox_shap)),]%>%
  forestplot(labeltext = tabletext,
             is.summary = summary,
             clip = c(0.3, 2.8), 
             hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:5, col = "#000044")
                      
                               #"9" = gpar(lwd=1)
                               ),
             xlog = FALSE,
             boxsize=0.3,
             graph.pos=3,
             colgap=unit(3, 'mm'),
             graphwidth=unit(34, 'mm'),
             lwd.ci=2,
             lwd.xaxis=2,
             zero = 1,
             xticks = seq(0.5, 2.5, 0.5), 
             #mar = unit(rep(10, times = 4), "mm"),
             col = fpColors(box = "royalblue",
                            line = "darkblue", 
                            summary = "royalblue"))


```


# Harrell's C-index on test data

We need to fit the model using training data and then using the coefficients (i.e. betas) to predict on test data then obtain the Harrell's C-index.

```{r training baseline}

eRFs <- c("TEU_BrCa_100k_PRS_quint","TEU_BrCa_313_PRS_quint","TEU_BaC_AgeAtRec","Imp_BodyFatMass","FSF_MenopauseAge","TEU_Alc_DailyAlcUnits","TEU_FirstBirthAgeCat","TEU_FaH_BrCa" ,  "PhA_METsWkAllAct" ,"G03FA", "FSF_PeriodAge","BBC_IGF1_Result" ,"BBC_TES_Result", "FSF_NLiveBirths" ,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(eRFs, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

pooled <- pool(rmodel)

# Copy one of the fitted models fit to
#   one of the imputed datasets
pooled_1st = rmodel$analyses[[1]]
# Replace the fitted coefficients with the pooled
#   estimates (need to check they are replaced in
#   the correct order)
pooled_1st$coefficients = summary(pooled)$estimate

```

```{r training new model 1}

varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel_m1 <- with(comp_long1, coxph(as.formula(formula)))

pooled_m1 <- pool(rmodel_m1)

# Copy one of the fitted models fit to
#   one of the imputed datasets
pooled_m1_1st = rmodel_m1$analyses[[1]]
# Replace the fitted coefficients with the pooled
#   estimates (need to check they are replaced in
#   the correct order)
pooled_m1_1st$coefficients = summary(pooled_m1)$estimate

```



```{r}
# transfer test to long
test_long <- complete(comp_long1_test,"long")

test_long <- test_long%>%
  mutate(baseline_pi=predict(pooled_1st,newdata = test_long,type = 'lp'),
         m1_pi=predict(pooled_m1_1st,newdata=test_long,type='lp'))


```


```{r}


C_index=test_long%>%group_by(.imp)%>%
  summarise(., C_index_baseline=survConcordance(Surv(TEU_BrCa_time,TEU_BrCa_status)~baseline_pi)$concordance,
            C_index_m1=survConcordance(Surv(TEU_BrCa_time,TEU_BrCa_status)~m1_pi)$concordance)

pander(as.data.frame(C_index),caption = "Harrell's C-index of 2 models on test data")

```

Median of C-index for baseline model is `r median(C_index$C_index_baseline)` and for new model 1 is `r median(C_index$C_index_m1)`.





















