---
title: "MLforBrCa Manuscript tables"
author: "Xiaonan Liu"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  word_document:
      reference_docx: "K:/TEU/TEU_Guides/TEU_DocStyle_Rmd_2020.dotx"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.pos = 'H')

library(kableExtra)
library(knitr)
library(yaml)
library(here)
library(ggplot2)
library(tidyr)
library(DiagrammeR)
library(DiagrammeRsvg)
library(magrittr)
library(svglite)
library(rsvg)
library(png)
library(grid)
library(dplyr)
library(survival)
library(survminer)
library(naniar)
library(summarytools)
library(rsample)      # data splitting 
library(gbm)          # basic implementation
library(xgboost)      # a faster implementation of gbm
library(caret)        # an aggregator package for performing many machine learning models
library(h2o)          # a java-based platform
library(pdp)          # model visualization
library(lime)         # model visualization
library(vip)          # Feature importance visualisation
library(rms)
library(mice)
library(shiny)
library(pander)
library(arsenal)
library(gtools)
library(ggeffects)
library(mitml)
library(forestplot)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('missing', '')

knitr::opts_knit$set(root.dir = here::here())
config = yaml.load_file(here::here("./config.yml"))
source(here::here(config$functions$JC))
source(here::here(config$functions$descriptive))

tot<-readRDS(here::here(file.path(config$data$derived,"tot_20220124.rds")))
tot_train<-readRDS(here::here(file.path(config$data$derived,"tot_train.rds")))
tot_test<-readRDS(here::here(file.path(config$data$derived,"tot_test.rds")))

xgboost_SHAP<-read.csv(here::here(file.path(config$outputs$outputs,"XGBoost_SHAP.csv")))

#load(here::here(file.path(config$data$derived,"imp_pre.rds")))
load(here::here(file.path(config$data$derived,"imp_post.rds")))
load(here::here(file.path(config$data$derived,"imp_post_derived.rds")))
load(here::here(file.path(config$data$derived,"imp_post_derived_scaled.rds")))
```

```{r Data extraction,include=FALSE}

source(file.path(config$scripts$cleaning, "dataset_generator.R"))

pretty_names <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type="list")
pretty_func <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type = "function")

pretty_names$TEU_FirstBirthAgeCat="Age at first birth (Categorical)"
pretty_names$TEU_Alc_DailyAlcUnits="Daily alcohol intake"
pretty_names$TEU_BrCa_100k_PRS="$$PRS_{120k}$$"
pretty_names$TEU_BrCa_313_PRS="$$PRS_{313}$$"
pretty_names$TEU_BrCa_100k_PRS_quintiles="$$PRS_{120k}$$ quintiles"
pretty_names$TEU_BrCa_313_PRS_quintiles="$$PRS_{313}$$ quintiles"
pretty_names$TEU_BrCa_313_PRS_percent="$$PRS_{313}$$ percentiles"
pretty_names$TEU_BrCa_100k_PRS_quint=pretty_names$TEU_BrCa_100k_PRS_quintiles
pretty_names$TEU_BrCa_313_PRS_quint=pretty_names$TEU_BrCa_313_PRS_quintiles
pretty_names$G03FA="HRT user"

```

# Table 1 (Descriptive Stats)

Here I presented the descriptive statistics of variables fitted in the model (except genetic arrays and 10 PCs) on whole population (i.e. training + test data).


```{r start}

imp_features<-c(
  xgboost_SHAP$Var_name[c(1:5,7:20)],
  # Because FaH of BrCa var name is in a different format
  "TEU_FaH_BrCa",
  # established RFs
  "BSM_BMI", "PhA_METsWkAllAct", "G03FA","FSF_PeriodAge",
   "FSF_NLiveBirths" 
)


```

```{r high cor}
# Removed BMI
imp_features<-imp_features[!grepl("BSM_BMI",imp_features)]

```

```{r}

tot<-tot%>%
  mutate(TEU_FirstBirthAgeCat=factor(case_when(
    # If no live births given, assign "No births"
    FSF_NLiveBirths==0 ~ "No Births",
    FSF_NLiveBirths>0 & TEU_FirstBirthAge<20 ~ "<20",
    FSF_NLiveBirths>0 & TEU_FirstBirthAge>=20 & TEU_FirstBirthAge<30 ~ "20-30",
    FSF_NLiveBirths>0 & TEU_FirstBirthAge>=30 & TEU_FirstBirthAge<40 ~ "30-40",
    FSF_NLiveBirths>0 & TEU_FirstBirthAge>=40 ~ ">=40",
    TRUE ~ NA_character_
  ),levels=c("No Births","<20","20-30","30-40",">=40"))
  )%>%
  # PRS quintiles
  mutate(TEU_BrCa_100k_PRS_quint=quantcut(TEU_BrCa_100k_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')),
         TEU_BrCa_313_PRS_quint=quantcut(TEU_BrCa_313_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')))%>%
  # Scale up PRS
  mutate(TEU_BrCa_100k_PRS=TEU_BrCa_100k_PRS*115300*2,
         TEU_BrCa_313_PRS=TEU_BrCa_313_PRS*305*2)

# Replace Father death age and age at first birth with the manipulated ones 

imp_features=replace(imp_features,imp_features=="TEU_FirstBirthAge","TEU_FirstBirthAgeCat")
#imp_features=replace(imp_features,imp_features=="TEU_BrCa_100k_PRS","TEU_BrCa_100k_PRS_quint")
#imp_features=replace(imp_features,imp_features=="TEU_BrCa_313_PRS","TEU_BrCa_313_PRS_quint")

```


```{r Descrp stats,results='asis'}

my_controls <- tableby.control(
    test = F,
    total = T,
    #numeric.test = "kwt", cat.test = "chisq",
    numeric.stats = c("medianq1q3", "N"), 
    cat.stats = c("countpct", "N"),
    stats.labels = list(
      #meansd = "Mean (SD)",
      medianq1q3 = "Median (IQR)",
      #range = "Min - Max",
      N = "N",
      Npct="N (Pct)"
    ),
    digits = 2L
  )

# Analysis vars (except Genetic array, 10 PCs)
varlist <- c(imp_features,"TEU_BrCa_status")

# Descrp stats by BrCa status


table<-tableby(TEU_BrCa_status~.,data=tot%>%select(all_of(varlist))%>%mutate(G03FA=factor(G03FA,levels = c("0","1"),labels = c("No","Yes"))),control=my_controls)


sumtab=summary(table,labelTranslations = pretty_names,title=paste0('Table 1. Descriptive statistics of analysis population by breast cancer status (N= ',nrow(tot),")"))

sumtab
```

```{r,eval=FALSE}

df<-as.data.frame(table)

df=df%>%group_by(variable)%>%
  mutate(label_new=ifelse(label=="Median (IQR)",dplyr::first(label),label))


```

# Table 2 (Cox model)

Cox model for post-menopausal women after MI. 

```{r}

imp_features<-c(
  xgboost_SHAP$Var_name[c(1:5,7:20)],
  # Because FaH of BrCa var name is in a different format
  "TEU_FaH_BrCa",
  # established RFs
  "BSM_BMI", "PhA_METsWkAllAct", "G03FA","FSF_PeriodAge",
   "FSF_NLiveBirths" 
)

##
imp_features<-imp_features[!grepl("BSM_BMI",imp_features)]

# Replace Father death age and age at first birth with the manipulated ones 

imp_features=replace(imp_features,imp_features=="TEU_FirstBirthAge","TEU_FirstBirthAgeCat")

# Transform the variables fitted in the model
imp_features=replace(imp_features,imp_features=="TEU_Alc_WeeklyAlcUnits","TEU_Alc_DailyAlcUnits")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_100k_PRS","TEU_BrCa_100k_PRS_quint")
imp_features=replace(imp_features,imp_features=="TEU_BrCa_313_PRS","TEU_BrCa_313_PRS_quint")

```


```{r Baseline model}

eRFs <- c("TEU_BrCa_100k_PRS_quint","TEU_BrCa_313_PRS_quint","TEU_BaC_AgeAtRec","Imp_BodyFatMass","FSF_MenopauseAge","TEU_Alc_DailyAlcUnits","TEU_FirstBirthAgeCat","TEU_FaH_BrCa" ,  "PhA_METsWkAllAct" ,"G03FA", "FSF_PeriodAge","BBC_IGF1_Result" ,"BBC_TES_Result", "FSF_NLiveBirths" ,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(eRFs, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_baseline <- printMIresults(df=comp_long1$data, varlist=eRFs, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#View(routput_baseline)
#kable(routput_baseline)%>%
  #kable_styling(bootstrap_options = c("striped", "hover")) 
```


```{r}

post_long1<-complete(comp_long1,"long")

pool<-post_long1%>%
  group_by(.imp)%>%
  summarise(.,C_index=concordance(coxph(formula=as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")))$concordance)

```

Concordance index of baseline model (median of C-index from each imputation dataset): `r median(pool$C_index)`

```{r New Model 1}

varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel_m1 <- with(comp_long1_scaled, coxph(as.formula(formula)))

routput_m1 <- printMIresults(df=comp_long1_scaled$data, varlist=varlist, modeloutput=summary(pool(rmodel_m1)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#kable(routput_m1)%>%
 # kable_styling(bootstrap_options = c("striped", "hover")) 
```

```{r}

pool2<-post_long1%>%
  group_by(.imp)%>%
  summarise(.,C_index=concordance(coxph(formula=as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")))$concordance)

```

Concordance index of New model 1 (median of C-index from each imputation dataset): `r median(pool2$C_index)`

```{r forest plot,eval=FALSE}

# Change order of FaH so corresponding to the SHAP order
present=setdiff(imp_features,"TEU_FaH_BrCa")
present <- append(present, values = "TEU_FaH_BrCa", after = match("TEU_Alc_DailyAlcUnits", present) - 1)         

# Add unit to features 
pretty_names$BBC_TES_Result="Testosterone,nmol/L"
pretty_names$FSF_MenopauseAge="Age at menopause,years"
pretty_names$TEU_Alc_DailyAlcUnits="Daily alcohol intake,units"
pretty_names$BBC_BUN_Result="Plasma urea,mmol/L"
pretty_names$Imp_MetRate="Basal metabolic rate,KJ"
pretty_names$BBC_PHOS_Result="Plasma phosphate,mmol/L"
pretty_names$BBC_IGF1_Result="IGF-1,nmol/L"
pretty_names$Uri_Sodium="Sodium in urine,mmol/L"
pretty_names$BlA_RedBCCount="Red blood cell count,10^12/L"
pretty_names$BBC_AST_Result="Aspartate aminotransferase,U/L"
pretty_names$TEU_FirstBirthAgeCat="Age at first birth,years (Categorical)"
pretty_names$Uri_Creat="Creatinine (enzymatic) in urine,mcmol/L"
pretty_names$BlA_MonocytCount="Monocytes count,10^9/L"
pretty_names$Imp_BodyFatMass="Whole body fat mass,Kg"
pretty_names$BBC_ALP_Result="Alkaline phosphatase,U/L"
pretty_names$BBC_CRP_Result="C-reactive protein,mg/L"
pretty_names$FSF_PeriodAge="Age at menarche,years"
pretty_names$PhA_METsWkAllAct="Summed MET minutes per week"
pretty_names$TEU_BaC_AgeAtRec="Age at recruitment,years"


m1_forplot <- printMIresults(df=comp_long1_scaled$data, varlist=present, modeloutput=summary(pool(rmodel_m1)),
                                pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE,forplot = TRUE)

cox_m1<-m1_forplot%>%
  # Create HR (95% CI)
  mutate(HR_CI=ifelse(is.na(L_CI),NA_character_,paste0(pretty_dp(HR_num,2)," ",pretty_confint(L_CI, U_CI, dp=2))))

cox_m1$HR_CI[is.na(cox_m1$HR_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- "1"
cox_m1$HR_num[is.na(cox_m1$HR_num) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$L_CI[is.na(cox_m1$L_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$U_CI[is.na(cox_m1$U_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1

# Hacky tweak so the cox model names correpsond to SHAP names
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{120k}$$ quintiles**"]="TEU_BrCa_100k_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{313}$$ quintiles**"]="TEU_BrCa_313_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**Family history of BrCa**"]="TEU_FaH_BrCa_Family history of BrCa"
cox_m1$IDcol[cox_m1$IDcol=="**Age at first birth,years (Categorical)**"]="TEU_FirstBirthAge"
cox_m1$IDcol[cox_m1$IDcol=="TEU_Alc_DailyAlcUnits"]="TEU_Alc_WeeklyAlcUnits"

# Add space for levels of categorical vars
cox_m1<-cox_m1%>%
  mutate(Coefficient=ifelse(!str_detect(Coefficient,fixed("**")),paste0("       ",Coefficient),Coefficient))

#test<-cox_m1
#test$Coefficient[c(2:6,8:12,17,18,28,32)]<-paste0("       ",test$Coefficient[c(2:6,8:12,17,18,28,32)])

# Prepare SHAP 

shap<-xgboost_SHAP[1:20,]%>%
  select(Var_name,SHAP)%>%
  #mutate(norm_SHAP=(SHAP-min(SHAP))/(max(SHAP)-min(SHAP)))%>%
  mutate(SHAP_pretty=pretty_dp(SHAP,2))

#shap$Var_name[shap$Var_name=="TEU_FaH_BrCa_Family history of BrCa"]="TEU_FaH_BrCa"
#shap$Var_name[shap$Var_name=="TEU_BrCa_100k_PRS"]="TEU_BrCa_100k_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_BrCa_313_PRS"]="TEU_BrCa_313_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_FirstBirthAge"]="TEU_FirstBirthAgeCat"
#shap$Var_name[shap$Var_name=="TEU_Alc_WeeklyAlcUnits"]="TEU_Alc_DailyAlcUnits"
#shap$Var_name2=preparecoefflist_2col(df=comp_long1$data,varname = shap$Var_name,pretty_names = pretty_names)

# Left join 

cox_shap<-left_join(cox_m1,shap,by=c("IDcol"="Var_name"))%>%
  select(Coefficient,SHAP_pretty,HR_CI,p,HR_num,L_CI,U_CI)%>%
  mutate(summary=FALSE)%>%
  mutate(Coefficient=str_remove_all(Coefficient,fixed("**")))%>%
  add_row(Coefficient = "Features", SHAP_pretty="mean(|SHAP value|)",HR_CI="HR (95% CI)",p="p-value", summary=TRUE,.before = 1)%>%
  rename(mean=HR_num,lower=L_CI,upper=U_CI)
  


# initialize plot
#tiff(file.path(config$outputs$outputs,"forestplot_A.tiff"),  units = "in", width = 7, height = 25, res = 300)

# make plot

tabletext <- list(
 c("Features",append(list(expression(PRS["120k"]~quintiles)),cox_shap$Coefficient[3:7]),append(list(expression(PRS["313"]~quintiles)),cox_shap$Coefficient[9:21])),
  c(list(expression(SHAP["ma"])),cox_shap$SHAP_pretty[2:21]),
  cox_shap$HR_CI[1:21],
  cox_shap$p[1:21]
)



cox_shap[1:21,]%>%
  forestplot(labeltext = tabletext, 
             is.summary = summary,
             clip = c(0.3, 2.8), 
             hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:5, col = "#000044") 
                               #"3" = gpar(lwd=1),
                               #"9" = gpar(lwd=1),
                               #"18" = gpar(lwd=1)
                               ),
             xlog = FALSE,
             boxsize=0.3,
             graph.pos=3,
             colgap=unit(3, 'mm'),
             graphwidth=unit(34, 'mm'),
             lwd.ci=2,
             lwd.xaxis=2,
             zero = 1,
             xticks = seq(0.5, 2.5, 0.5), 
             #mar = unit(rep(10, times = 4), "mm"),
             col = fpColors(box = "royalblue",
                            line = "darkblue", 
                            summary = "royalblue"))

# save plot
#dev.copy(png,file.path(config$outputs$outputs,"forestplot.png"))
#dev.off()

## Too long, has to be split into 2
#tiff(file.path(config$outputs$outputs,"forestplot_B.tiff"),  units = "in", width = 13, height = 50, res = 300)

tabletext <- list(
 cox_shap$Coefficient[c(1,22:nrow(cox_shap))],
  c(list(expression(SHAP["ma"])),cox_shap$SHAP_pretty[22:nrow(cox_shap)]),
  cox_shap$HR_CI[c(1,22:nrow(cox_shap))],
  cox_shap$p[c(1,22:nrow(cox_shap))]
)



# make plot
cox_shap[c(1,22:nrow(cox_shap)),]%>%
  forestplot(labeltext = tabletext,
             is.summary = summary,
             clip = c(0.3, 2.8), 
             hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:5, col = "#000044")
                      
                               #"9" = gpar(lwd=1)
                               ),
             xlog = FALSE,
             boxsize=0.3,
             graph.pos=3,
             colgap=unit(3, 'mm'),
             graphwidth=unit(34, 'mm'),
             lwd.ci=2,
             lwd.xaxis=2,
             zero = 1,
             xticks = seq(0.5, 2.5, 0.5), 
             #mar = unit(rep(10, times = 4), "mm"),
             col = fpColors(box = "royalblue",
                            line = "darkblue", 
                            summary = "royalblue"))

# save plot
#dev.copy(png,file.path(config$outputs$outputs,"forestplot.png"))
#dev.off()

```


```{r merge}

# Merge baseline and New model1 analysis tgt
output<-full_join(routput_baseline,routput_m1,by=c("IDcol"))%>%
  select(Coefficient.y,HR.x,`95% CI.x`,p.x,HR.y,`95% CI.y`,p.y)%>%
  `colnames<-`(c("Coefficient","HR","95% CI","p","HR","95% CI","p"))

pander(output,caption=paste0("Table 2. Cox regression of time until breast cancer (",sum(comp_long1$data$TEU_BrCa_status)," events)"))

```



# Interaction Model 

Age* PRS interaction. From SHAP dependence plots: for older age (60+), having a relative higher PRS exaggerates age effect on developing breast cancer whereas for younger age (53-60), having a relative lower PRS exaggerate age effect on developing breast cancer.

**BrCa 100k PRS**: 

```{r}
# 100k PRS * age
varlist <- c(imp_features,"TEU_BrCa_100k_PRS_quint:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_int1 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)

pander(routput_int1,caption="New model 1 + Age*BrCa 100k PRS (quintiles)")

```

```{r}
# Overall p-value


LR1<-anova(rmodel_m1,rmodel,method = 'D2',use = 'likelihood')

p1<-pretty_pval(LR1$out$`2 ~~ 1`$result[4])

```

Interaction p-value is `r p1`

Visual plots on relative hazard (based on one random imputation dataset): 'K:\\TEU\\MLforBrCa\\Stats_Outputs\\Marginal_PRS120k.png'



```{r int plots,eval=FALSE}
# Plot (Age*prs)

# Note: For some reason, the formula with paste above doesn't work in this loop!

predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result + TEU_BrCa_100k_PRS_quint:TEU_BaC_AgeAtRec +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BaC_AgeAtRec [all]","TEU_BrCa_100k_PRS_quint"))
})

# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)


plot(predictions[[1]])+
  labs(x=expression(bold("Age at recruitment, years")),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold(PRS["120k"]~quintiles)))+
  xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```

**BrCa 313 PRS**:

```{r}
# 313 PRS * age
varlist <- c(imp_features,"TEU_BrCa_313_PRS_quint:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel <- with(comp_long1, coxph(as.formula(formula)))

routput_int2 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)


pander(routput_int2,caption="New Model 1 + BrCa 313 PRS")


```

```{r}
# Overall p-value

LR2<-anova(rmodel_m1,rmodel,method = 'D2',use = 'likelihood')

p2<-pretty_pval(LR2$out$`2 ~~ 1`$result[4])

```

Interaction p-value is `r p2`.

Visual plots on relative hazard (based on one random imputation dataset): 'K:\\TEU\\MLforBrCa\\Stats_Outputs\\Marginal_PRS313.png'


```{r BrCa 313 int plots,eval=FALSE}
# Plot (Age*prs)

# Note: For some reason, the formula with paste above doesn't work in this loop!

predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status) ~ 
    TEU_BrCa_100k_PRS_quint + TEU_BrCa_313_PRS_quint + TEU_BaC_AgeAtRec + 
    Imp_BodyFatMass + FSF_MenopauseAge + TEU_Alc_DailyAlcUnits +
    TEU_FirstBirthAgeCat + TEU_FaH_BrCa +  PhA_METsWkAllAct +
    G03FA  + BBC_TES_Result +  FSF_PeriodAge + BBC_IGF1_Result +FSF_NLiveBirths+
    BBC_BUN_Result + Imp_MetRate + BBC_PHOS_Result + Uri_Sodium + BlA_RedBCCount +
    BBC_AST_Result + Uri_Creat + BlA_MonocytCount + BBC_ALP_Result + 
    BBC_CRP_Result + TEU_BrCa_313_PRS_quint:TEU_BaC_AgeAtRec +
    GeP_Array + GeP_PC_1 + GeP_PC_2 + GeP_PC_3 + GeP_PC_4 + GeP_PC_5 + 
    GeP_PC_6 + GeP_PC_7 + GeP_PC_8 + GeP_PC_9 + GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BaC_AgeAtRec [all]","TEU_BrCa_313_PRS_quint"))
})

# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)

plot(predictions[[1]])+
  labs(x=expression(bold("Age at recruitment, years")),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold(PRS["313"]~quintiles)))+
  xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))

```




