---
title: "MLforBrCa: Sensitivity analyses (i.e. Supplementary Material)"
author: "Xiaonan Liu"
date: "2023-04-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.pos = 'H')

library(kableExtra)
library(knitr)
library(yaml)
library(here)
library(ggplot2)
library(tidyr)
library(DiagrammeR)
library(DiagrammeRsvg)
library(magrittr)
library(svglite)
library(rsvg)
library(png)
library(grid)
library(dplyr)
library(survival)
library(survminer)
library(naniar)
library(summarytools)
library(rsample)      # data splitting 
library(gbm)          # basic implementation
library(caret)        # an aggregator package for performing many machine learning models
library(pdp)          # model visualization
library(lime)         # model visualization
library(vip)          # Feature importance visualisation
library(rms)
library(mice)
library(pander)
library(arsenal)
library(gtools)
library(ggeffects)
#library(mitml)
library(forestplot)
library(rcompanion)
library(splines) #rcs
library(riskRegression)
library(glmnet)
library(plotmo) # for plot_glmnet

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('missing', '')

knitr::opts_knit$set(root.dir = here::here())
config = yaml.load_file(here::here("./config.yml"))
source(here::here(config$functions$JC))
#source(here::here(config$functions$descriptive))

#tot<-readRDS(here::here(file.path(config$data$derived,"tot_20220124.rds")))
tot_train<-readRDS(here::here(file.path(config$data$derived,"tot_train.rds")))
tot_test<-readRDS(here::here(file.path(config$data$derived,"tot_test.rds")))

xgboost_SHAP<-read.csv(here::here(file.path(config$outputs$outputs,"ML coxloss/XGBoost_Cox_SHAP.csv")))

load(here::here(file.path(config$data$derived,"Cox/imp_post.rds")))
load(here::here(file.path(config$data$derived,"Cox/imp_post_derived.rds")))
load(here::here(file.path(config$data$derived,"Cox/imp_post_derived_scaled.rds")))


load(here::here(file.path(config$data$derived,"Cox/imp_post_test.rds")))
load(here::here(file.path(config$data$derived,"Cox/imp_post_test_derived.rds")))
load(here::here(file.path(config$data$derived,"Cox/imp_post_test_scaled.rds")))

data<-readRDS(here::here(file.path(config$data$derived,"Otherethnic.rds")))
```

```{r Data extraction,include=FALSE}

source(file.path(config$scripts$cleaning, "dataset_generator.R"))

pretty_names <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type="list")
pretty_func <- pretty_switch(field_definitions=c(TEU_SPECS$BrCa_PRS,TEU_SPECS$HES_CaR), return_type = "function")


pretty_names$TEU_BrCa_100k_PRS="$$PRS_{120k}$$"
pretty_names$TEU_BrCa_313_PRS="$$PRS_{313}$$"
pretty_names$G03FA="HRT user"

# Add unit to features 
pretty_names$BBC_TES_Result="Testosterone,nmol/L"
pretty_names$FSF_MenopauseAge="Age at menopause,years"
pretty_names$TEU_Alc_DailyAlcUnits="Daily alcohol intake,units"
pretty_names$BBC_BUN_Result="Plasma urea,mmol/L"
pretty_names$Imp_MetRate="Basal metabolic rate,KJ"
pretty_names$BBC_PHOS_Result="Plasma phosphate,mmol/L"
pretty_names$BBC_IGF1_Result="IGF-1,nmol/L"
pretty_names$Uri_Sodium="Sodium in urine,mmol/L"
pretty_names$BlA_RedBCCount="Red blood cell count,10^12/L"
pretty_names$BBC_AST_Result="Aspartate aminotransferase,U/L"
pretty_names$TEU_FirstBirthAgeCat="Age at first birth,years (Categorical)"
pretty_names$Uri_Creat="Creatinine (enzymatic) in urine,mcmol/L"
pretty_names$BlA_MonocytCount="Monocytes count,10^9/L"
pretty_names$Imp_BodyFatMass="Whole body fat mass,Kg"
pretty_names$BBC_ALP_Result="Alkaline phosphatase,U/L"
pretty_names$BBC_CRP_Result="C-reactive protein,mg/L"
pretty_names$FSF_PeriodAge="Age at menarche,years"
pretty_names$PhA_METsWkAllAct="Summed MET minutes per week"
pretty_names$TEU_BaC_AgeAtRec="Age at recruitment,years"
pretty_names$BBC_GGT_Result="Gamma glutamyltransferase,U/L"
pretty_names$BSM_BMI="BMI, kg/m^2"
pretty_names$`TEU_FaH_BrCaNo family history of BrCa`="No family history of breast cancer"
```




# Correlation matrix (on training data)

```{r imp features}

imp_features<-c(
  xgboost_SHAP$Var_name[c(1:8,10:20)],
  # Because FaH of BrCa var name is in a different format
  "TEU_FaH_BrCa",
  # established RFs
  "BSM_BMI", "G03FA","FSF_PeriodAge",
   "FSF_NLiveBirths" 
)

#sapply(imp_features,function(i) pretty_names[[i]])
```


```{r cor,cache=TRUE}
cor=mixed_assoc(tot_train%>%select(all_of(imp_features)))

cor_df<-cor%>%
  mutate(
    xy=paste0(x,y),
    yx=paste0(y,x),# don't want to show duplicates
    assoc=round(assoc,2))%>%
  filter(xy!=yx)%>%
  filter(assoc>0.5|assoc< -0.5)%>%
  rowwise()%>%
  mutate(x=pretty_func(x),
         y=pretty_func(y))%>%
  select(x,y,assoc)%>%
  arrange(desc(assoc))

rownames(cor_df)=NULL

# Transfer to correlation matrix format
#df1 <- as.data.frame.matrix(xtabs(assoc ~ ., cor_df))

# pretty names
#df1<-tibble::rownames_to_column(df1, "VALUE")%>%
  #rowwise()%>%
  #mutate(VALUE=pretty_func(VALUE))

#names(df1)<-sapply(names(df1),function(i) pretty_func(i))
# Correlation matrix is too big for display

pander(cor_df,caption = "Pairwise correlation matrix among the union of top 20 features and other established predictors using the training data. Only pairs with absolute correlation above 0.5 were displayed.")

```


# Cox models using test data

```{r post-processing scale,eval=FALSE}
# Post-hoc: Scale variables with HR CI (1,1) to show wider CI in forest plot
# Scale alcohol per week to per day
# Create quintiles for PRS
long1<-complete(imp_post_test,"long",include=TRUE)
comp_long1_test_scaled<-long1%>%
  mutate(
    TEU_Alc_DailyAlcUnits=TEU_Alc_WeeklyAlcUnits/7,
    )%>%
  group_by(.imp)%>%
  mutate(
    # Scale variables by mean and sd within each imp
    Imp_MetRate=scale_this(Imp_MetRate),
    Uri_Sodium=scale_this(Uri_Sodium),
    Uri_Creat=scale_this(Uri_Creat),
    BBC_GGT_Result=scale_this(BBC_GGT_Result),
    BBC_ALP_Result=scale_this(BBC_ALP_Result),
    PhA_METsWkAllAct=scale_this(PhA_METsWkAllAct)
  )
  
comp_long1_test_scaled<-as.mids(comp_long1_test_scaled)
save(comp_long1_test_scaled,file=file.path(config$data$derived,'Cox/imp_post_test_scaled.rds'))
```


```{r Baseline model test data}

eRFs <- c("TEU_BrCa_100k_PRS","TEU_BrCa_313_PRS","TEU_BaC_AgeAtRec","BSM_BMI","FSF_MenopauseAge","TEU_Alc_DailyAlcUnits","TEU_FirstBirthAgeCat","TEU_FaH_BrCa" ,  "PhA_METsWkAllAct" ,"G03FA", "FSF_PeriodAge","BBC_IGF1_Result" ,"BBC_TES_Result", "FSF_NLiveBirths" ,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(eRFs, collapse="+"))

rmodel <- with(comp_long1_test_scaled, coxph(as.formula(formula)))

routput_baseline_test <- printMIresults(df=comp_long1_test_scaled$data, varlist=eRFs, modeloutput=summary(pool(rmodel)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#View(routput_baseline)
#kable(routput_baseline)%>%
  #kable_styling(bootstrap_options = c("striped", "hover")) 
```

```{r New Model 1 test data}

varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel_m1_test <- with(comp_long1_test_scaled, coxph(as.formula(formula)))

routput_m1_test <- printMIresults(df=comp_long1_test_scaled$data, varlist=varlist, modeloutput=summary(pool(rmodel_m1_test)),
                              pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE)

#kable(routput_m1)%>%
  #kable_styling(bootstrap_options = c("striped", "hover")) 
```

```{r Merge}

output_test<-full_join(routput_baseline_test,routput_m1_test,by=c("IDcol"))%>%
  select(Coefficient.y,HR.x,`95% CI.x`,p.x,HR.y,`95% CI.y`,p.y)%>%
  `colnames<-`(c("Coefficient","HR","95% CI","p","HR","95% CI","p"))

pander(output_test,caption=paste0("Cox regression of time until breast cancer using test data (",sum(comp_long1_test_scaled$data$TEU_BrCa_status)," events)"))

```


For ease of viewing: 

```{r}

routput_m1<-full_join(routput_m1_training,routput_m1_test,by="IDcol",suffix=c(".training",".test"))

pander(routput_m1%>%select(!c(IDcol,Coefficient.test)),caption="New Cox model fitted in training and test data respectively.")

```

# Exclude first 2 yrs FU (Training)

To further investigate blood count, biochemistry, urine assays variables (in New Model 2), we would like to restrict our analysis population to people with 2 or more years follow up and see if they are still significant. The logic behind this is to see if significance were due to reverse causation. 

Out of `r nrow(tot_train)` post-menopausal women, there were `r tot_train%>%filter(TEU_BrCa_time>=2)%>%nrow` with 2 or more years follow up.

```{r SA New Model 1,eval=FALSE}

# Transform to long first 
post.long <- mice::complete(imp_post,"long",include = T)

post.long.sub <- post.long[which(post.long$TEU_BrCa_time >=2),]
# Post-hoc: Scale variables with HR CI (1,1) to show wider CI in forest plot

post.long.sub<-post.long.sub%>%
  mutate(
    TEU_Alc_DailyAlcUnits=TEU_Alc_WeeklyAlcUnits/7,
    )%>%
  group_by(.imp)%>%
  mutate(
    # Scale variables by mean and sd within each imp
    Imp_MetRate=scale_this(Imp_MetRate),
    Uri_Sodium=scale_this(Uri_Sodium),
    Uri_Creat=scale_this(Uri_Creat),
    BBC_GGT_Result=scale_this(BBC_GGT_Result),
    BBC_ALP_Result=scale_this(BBC_ALP_Result),
    PhA_METsWkAllAct=scale_this(PhA_METsWkAllAct)
  )


# Create mids object
imp_post_sub <- as.mids(post.long.sub)

##
varlist <- c(imp_features,"GeP_Array",paste(paste0("GeP_PC_",1:10)))

formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))

rmodel_SA <- with(imp_post_sub, coxph(as.formula(formula)))

#routput_post_sub <- printMIresults(df=imp_post_sub$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              #pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)

#pander(routput_post_sub)
```


```{r forest plot SA,eval=FALSE}

# Change order of FaH so corresponding to the SHAP order
present=setdiff(imp_features,"TEU_FaH_BrCa")
present <- append(present, values = "TEU_FaH_BrCa", after = match("Imp_MetRate", present) - 1)         

m1_forplot <- printMIresults(df=imp_post_sub$data, varlist=present, modeloutput=summary(pool(rmodel_SA)),
                                pretty_names=pretty_names, onecol=TRUE, IDcol=TRUE,forplot = TRUE)

cox_m1<-m1_forplot%>%
  # Create HR (95% CI)
  mutate(HR_CI=ifelse(is.na(L_CI),NA_character_,paste0(pretty_dp(HR_num,2)," ",pretty_confint(L_CI, U_CI, dp=2))))

cox_m1$HR_CI[is.na(cox_m1$HR_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- "1"
cox_m1$HR_num[is.na(cox_m1$HR_num) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$L_CI[is.na(cox_m1$L_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1
cox_m1$U_CI[is.na(cox_m1$U_CI) & (cox_m1$IDcol != cox_m1$Coefficient & !is.na(cox_m1$Coefficient))] <- 1

# Hacky tweak so the cox model names correpsond to SHAP names
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{120k}$$ quintiles**"]="TEU_BrCa_100k_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**$$PRS_{313}$$ quintiles**"]="TEU_BrCa_313_PRS"
cox_m1$IDcol[cox_m1$IDcol=="**Family history of BrCa**"]="TEU_FaH_BrCa_Family history of BrCa"
cox_m1$IDcol[cox_m1$IDcol=="**Age at first birth,years (Categorical)**"]="TEU_FirstBirthAge"
cox_m1$IDcol[cox_m1$IDcol=="TEU_Alc_DailyAlcUnits"]="TEU_Alc_WeeklyAlcUnits"

# Add space for levels of categorical vars
cox_m1<-cox_m1%>%
  mutate(Coefficient=ifelse(!str_detect(Coefficient,fixed("**")),paste0("       ",Coefficient),Coefficient))

#test<-cox_m1
#test$Coefficient[c(2:6,8:12,17,18,28,32)]<-paste0("       ",test$Coefficient[c(2:6,8:12,17,18,28,32)])

# Prepare SHAP 

shap<-xgboost_SHAP[1:20,]%>%
  select(Var_name,SHAP)%>%
  #mutate(norm_SHAP=(SHAP-min(SHAP))/(max(SHAP)-min(SHAP)))%>%
  mutate(SHAP_pretty=pretty_dp(SHAP,2))

#shap$Var_name[shap$Var_name=="TEU_FaH_BrCa_Family history of BrCa"]="TEU_FaH_BrCa"
#shap$Var_name[shap$Var_name=="TEU_BrCa_100k_PRS"]="TEU_BrCa_100k_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_BrCa_313_PRS"]="TEU_BrCa_313_PRS_quintiles"
#shap$Var_name[shap$Var_name=="TEU_FirstBirthAge"]="TEU_FirstBirthAgeCat"
#shap$Var_name[shap$Var_name=="TEU_Alc_WeeklyAlcUnits"]="TEU_Alc_DailyAlcUnits"
#shap$Var_name2=preparecoefflist_2col(df=comp_long1$data,varname = shap$Var_name,pretty_names = pretty_names)

# Left join 

cox_shap<-left_join(cox_m1,shap,by=c("IDcol"="Var_name"))%>%
  select(Coefficient,SHAP_pretty,HR_CI,p,HR_num,L_CI,U_CI)%>%
  mutate(summary=FALSE)%>%
  mutate(Coefficient=str_remove_all(Coefficient,fixed("**")))%>%
  add_row(Coefficient = "Features", SHAP_pretty="mean(|SHAP value|)",HR_CI="HR (95% CI)",p="p-value", summary=TRUE,.before = 1)%>%
  rename(mean=HR_num,lower=L_CI,upper=U_CI)
  


# initialize plot
#tiff(file.path(config$outputs$outputs,"forestplot_A.tiff"),  units = "in", width = 7, height = 25, res = 300)

# make plot

tabletext <- list(
 c("Features",list(expression(PRS["313"])),list(expression(PRS["120k"])),cox_shap$Coefficient[4:nrow(cox_shap)]),
  c(list(expression(SHAP["ma"])),cox_shap$SHAP_pretty[2:nrow(cox_shap)]),
  cox_shap$HR_CI[1:nrow(cox_shap)],
  cox_shap$p[1:nrow(cox_shap)]
)

# Note: for saving this super long forestplot, do not use the png function below, just manually export the plot with adjustment of width and height in the plots panel.
#png(file=file.path(config$outputs$outputs,"/ML coxloss/forestplot.png"),width=500*2.5,height=600*2)

cox_shap%>%
  forestplot(labeltext = tabletext, 
             is.summary = summary,
             clip = c(0.3, 2.8), 
             hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:5, col = "#000044") 
                               #"3" = gpar(lwd=1),
                               #"9" = gpar(lwd=1),
                               #"18" = gpar(lwd=1)
                               ),
             xlog = FALSE,
             boxsize=0.4,
             graph.pos=3,
             colgap=unit(3, 'mm'),
             graphwidth=unit(34, 'mm'),
             lwd.ci=2,
             lwd.xaxis=2,
             zero = 1,
             xticks = seq(0.5, 2.5, 0.5), 
             txt_gp = fpTxtGp(ticks=gpar(cex=1)), #change xticks font size
             #mar = unit(rep(10, times = 4), "mm"),
             col = fpColors(box = "royalblue",
                            line = "darkblue", 
                            summary = "royalblue"))

# save plot
#dev.off()

```


# Age PRS interaction


```{r}
# 100k PRS * age
varlist <- c(imp_features,"TEU_BrCa_100k_PRS:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))
formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))
rmodel_int1 <- with(comp_long1, coxph(as.formula(formula)))
#routput_int1 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
                              #pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)
#pander(routput_int1,caption="New model 1 + Age*BrCa 100k PRS (quintiles)")
```

```{r}
# Overall p-value
LR1<-anova(rmodel_m1_training,rmodel_int1,method = 'D2',use = 'likelihood')
p1<-pretty_pval(LR1$out$`2 ~~ 1`$result[4])
```

Interaction p-value is `r p1`



```{r int plots,eval=FALSE}
# Plot (Age*prs)
# Note: For some reason, the formula with paste above doesn't work in this loop!

# Note: below different from above because age was fitted categorical
predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status)~ TEU_BrCa_313_PRS+TEU_BrCa_100k_PRS+TEU_BaC_AgeCat+BBC_TES_Result+FSF_MenopauseAge+BBC_IGF1_Result+BBC_BUN_Result+TEU_Alc_DailyAlcUnits+Imp_MetRate+TEU_FirstBirthAgeCat+BBC_AST_Result+BBC_PHOS_Result+BBC_CRP_Result+Uri_Sodium+BlA_RedBCCount+BBC_GGT_Result+Uri_Creat+BBC_ALP_Result+PhA_METsWkAllAct+TEU_FaH_BrCa+BSM_BMI+G03FA+FSF_PeriodAge+FSF_NLiveBirths+TEU_BrCa_100k_PRS:TEU_BaC_AgeCat+GeP_Array+GeP_PC_1+GeP_PC_2+GeP_PC_3+GeP_PC_4+GeP_PC_5+GeP_PC_6+GeP_PC_7+GeP_PC_8+GeP_PC_9+GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BrCa_100k_PRS [all]","TEU_BaC_AgeCat"))
})
# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)
plot(predictions[[1]])+
  labs(x=expression(bold(PRS["120k"])),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold("Age at recruitment, years")))+
  #xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))
```

**BrCa 313 PRS**:

```{r}
# 313 PRS * age
varlist <- c(imp_features,"TEU_BrCa_313_PRS:TEU_BaC_AgeAtRec","GeP_Array",paste(paste0("GeP_PC_",1:10)))
formula <- paste0("Surv(TEU_BrCa_time, TEU_BrCa_status)~ ", paste(varlist, collapse="+"))
rmodel_int2 <- with(comp_long1, coxph(as.formula(formula)))
#routput_int2 <- printMIresults(df=comp_long1$data, varlist=varlist, modeloutput=summary(pool(rmodel)),
 #                             pretty_names=pretty_names, onecol=TRUE, IDcol=FALSE)
#pander(routput_int2,caption="New Model 1 + BrCa 313 PRS")
```

```{r}
# Overall p-value
LR2<-anova(rmodel_m1_training,rmodel_int2,method = 'D2',use = 'likelihood')
p2<-pretty_pval(LR2$out$`2 ~~ 1`$result[4])
```

Interaction p-value is `r p2`.



```{r BrCa 313 int plots,eval=FALSE}
# Plot (Age*prs)
# Note: For some reason, the formula with paste above doesn't work in this loop!

# Note formula below is different from above, age fitted categorical below
predictions <- lapply(1:10, function(i) {
  
  formula<-as.formula("Surv(TEU_BrCa_time, TEU_BrCa_status)~ TEU_BrCa_313_PRS+TEU_BrCa_100k_PRS+TEU_BaC_AgeCat+BBC_TES_Result+FSF_MenopauseAge+BBC_IGF1_Result+BBC_BUN_Result+TEU_Alc_DailyAlcUnits+Imp_MetRate+TEU_FirstBirthAgeCat+BBC_AST_Result+BBC_PHOS_Result+BBC_CRP_Result+Uri_Sodium+BlA_RedBCCount+BBC_GGT_Result+Uri_Creat+BBC_ALP_Result+PhA_METsWkAllAct+TEU_FaH_BrCa+BSM_BMI+G03FA+FSF_PeriodAge+FSF_NLiveBirths+TEU_BrCa_313_PRS:TEU_BaC_AgeCat+GeP_Array+GeP_PC_1+GeP_PC_2+GeP_PC_3+GeP_PC_4+GeP_PC_5+GeP_PC_6+GeP_PC_7+GeP_PC_8+GeP_PC_9+GeP_PC_10")
  
    m <- coxph(formula, data = complete(comp_long1, action = i))
    ggpredict(m, terms=c("TEU_BrCa_313_PRS [all]","TEU_BaC_AgeCat"))
})
# Don't think this pool_predictions is very reliable  
#pool_pred<-pool_predictions(predictions)
plot(predictions[[1]])+
  labs(x=expression(bold(PRS["313"])),y=expression(bold("Relative hazard, exp(Xbeta)")),title = "",
       color=expression(bold("Age at recruitment, years")))+
  #xlim(40,70)+
  #scale_color_discrete(labels=c("**Q1: Lowest score**","Q2","Q3","Q4","Q5: Highest score"))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))
```


# Stratified Cox model by age groups

Categorised age in 3 groups: [40,53), [53,62), [62,70) and performed stratified cox model by 3 age groups: 

* BrCa ~ PRS + Genetic Array + First 10 genetic PCs

Note: Originally we wanted to categorise PRS into percentiles according to Mavaddat2019 (i.e. <1%, 1-5%, ...); however, due to sample size of each age group, we ran into model convergence issue.

**BrCa 100k PRS:**

```{r}
df<-tot_train%>%
  mutate(agecat=cut(TEU_BaC_AgeAtRec,
                       breaks = c(40, 53, 62, 70),
                       labels = c("[40,53)", "[53,62)", "[62,70)"),
                       right = FALSE
    ),
  TEU_BrCa_100k_PRS=TEU_BrCa_100k_PRS*115300*2,
  TEU_BrCa_313_PRS=TEU_BrCa_313_PRS*305*2,
  PRS_100k=quantcut(TEU_BrCa_100k_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')),
  PRS_313=quantcut(TEU_BrCa_313_PRS,q=5,labels=c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')))
# Relevel so that average is the ref
#df <- within(df, PRS_100k_tertile <- relevel(PRS_100k_tertile, ref = "Average"))
#df <- within(df, PRS_313_tertile <- relevel(PRS_313_tertile, ref = "Average"))
propped(table(df$agecat))
RFs<-c("PRS_100k","GeP_Array",paste0("GeP_PC_",1:10))
formula<-as.formula(paste0("Surv(TEU_BrCa_time,TEU_BrCa_status)~", 
                           paste(RFs, collapse="+")))
cox_results=lapply(split(df, df$agecat),
       FUN = function(DF) {
         
         coxph(formula, DF)
       })
```



```{r}
tab1=printcoxresults(df,varlist = "PRS_100k",modeloutput = cox_results$`[40,53)`,pretty_names = pretty_names,forplot = TRUE)
tab1$agegrp="[40,53)"
tab2=printcoxresults(df,varlist =  "PRS_100k",modeloutput = cox_results$`[53,62)`,pretty_names = pretty_names,forplot=TRUE)
tab2$agegrp="[53,62)"
tab3=printcoxresults(df,varlist =  "PRS_100k",modeloutput = cox_results$`[62,70)`,pretty_names = pretty_names,forplot=TRUE)
tab3$agegrp="[62,70)"
tab=rbind(tab1,tab2,tab3)
kable(tab,caption = "Hazard Ratio of BrCa 100k PRS in different age groups")%>%
 kable_styling(bootstrap_options = c("striped", "hover")) 
# Visualise PRS effect SC by age
ggplot(tab, aes(fill=factor(Levels,levels = c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')), y=HR_num, x=agegrp)) + 
    geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.2,
                 position=position_dodge(.9)) +
  labs(x="Age at recruitment, years (Categorical)",y="Hazard Ratio with 95% CI",title = "") + 
  scale_fill_discrete(name = expression(bold(PRS["120k"]~quintiles)))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))
```


**BrCa 313 PRS:**

```{r}
RFs<-c("PRS_313","GeP_Array",paste0("GeP_PC_",1:10))
formula<-as.formula(paste0("Surv(TEU_BrCa_time,TEU_BrCa_status)~", 
                           paste(RFs, collapse="+")))
cox_results=lapply(split(df, df$agecat),
       FUN = function(DF) {
         
         coxph(formula, DF)
       })
```


```{r}
tab1=printcoxresults(df,varlist = "PRS_313",modeloutput = cox_results$`[40,53)`,pretty_names = pretty_names,forplot = TRUE)
tab1$agegrp="[40,53)"
tab2=printcoxresults(df,varlist =  "PRS_313",modeloutput = cox_results$`[53,62)`,pretty_names = pretty_names,forplot=TRUE)
tab2$agegrp="[53,62)"
tab3=printcoxresults(df,varlist =  "PRS_313",modeloutput = cox_results$`[62,70)`,pretty_names = pretty_names,forplot=TRUE)
tab3$agegrp="[62,70)"
tab=rbind(tab1,tab2,tab3)
kable(tab,caption = "Hazard Ratio of BrCa 313 PRS in different age groups")%>%
 kable_styling(bootstrap_options = c("striped", "hover")) 
# Visualise PRS effect SC by age
ggplot(tab, aes(fill=factor(Levels,levels = c('Q1: Lowest level','Q2','Q3','Q4','Q5: Highest level')), y=HR_num, x=agegrp)) + 
    geom_bar(position="dodge", stat="identity") +
  geom_errorbar(aes(ymin=LCI, ymax=UCI), width=.2,
                 position=position_dodge(.9)) +
  labs(x="Age at recruitment, years (Categorical)",y="Hazard Ratio with 95% CI",title = "") + 
  scale_fill_discrete(name = expression(bold(PRS["313"]~quintiles)))+
  theme(legend.position = "top",legend.text = element_text(size=12),
        axis.text = element_text(size=15))
```








